On Determinism of Game Engines used for Simulation-based Autonomous Vehicle Verification

### 2021-03-22 paper/cav_determinisim_main.tex
removing ighlights

{\color{red} \sc Ensure past/present is used consistently and appropriately throughout.}

@@

{\color{red} \sc Surely, a series of systematically designed experiments, each repeated X times, should be set up, where each experiment varies one of the suspected sources of non-determinism? Then, the analysis of the data from each experiment should reveal the actual sources of non-determinism for the given setting? In other words, we are aiming to fix as much as we can control (easily), and then we intentionally vary (ideally) single variables, e.g.\ the resource utilisation, to find out what makes a difference. We need a clear definition of the objectives of the experimental design, i.e.\ what one should vary and what one wants to ``nail down''.}

{\color{green!99} \sc The experiment design is based around a series of carefully selected tests that varies one of the sources of non-determinism whilst keeping all others parameters constant. Each test is repeated $n$ times and the analysis of the results provide a confidence with a degree of statistical certainty. By varying a single parameter and controlling all others, the simulation variance associated with each source of non-determinism can be found and addressed. }

@@

\subsubsection{Sample Size}
% Tests should be sufficiently repeated using statistical power~\cite{cohen2013statistical} to reveal any outlier errors that occur with low probability.\todo[inline]{Explain what this means.} 
% Histogram to show how sampling with position binning varies?
% \footnote{\label{note1}Experiments using the Unreal Engine not reported here for brevity but code and experimental results can be found at \url{https://github.com/TSL-UOB/AV-Determinism/tree/master/UnrealEngineTests}}
%
% {\color{red} \sc Again, separate the study from the method. This observation should really have been made in the section on ``Experimental System Config and Pre-Screening, to justify the figure of 1000 repeats.} 
It is recommended that the chosen sample size is determined empirically. 
%
{\color{green} We recommend monitoring variance while increasing the sample size in orders of magnitude
until there is confidence that $\max\sigma$ will not exceed the permissible variance for the verification process. 
%
Note that we suggest monitoring the maximum value of $\sigma$, not the average, because if even a single simulation run is outside of the permissible variance this may lead to false confidence in the verification result.}

>>>>

% {\color{red} \sc Ensure past/present is used consistently and appropriately throughout.}

@@

% {\color{red} \sc Surely, a series of systematically designed experiments, each repeated X times, should be set up, where each experiment varies one of the suspected sources of non-determinism? Then, the analysis of the data from each experiment should reveal the actual sources of non-determinism for the given setting? In other words, we are aiming to fix as much as we can control (easily), and then we intentionally vary (ideally) single variables, e.g.\ the resource utilisation, to find out what makes a difference. We need a clear definition of the objectives of the experimental design, i.e.\ what one should vary and what one wants to ``nail down''.}

% {\color{green!99} \sc }
The experiment design is based around a series of carefully selected tests that varies one of the sources of non-determinism whilst keeping all others parameters constant. Each test is repeated $n$ times and the analysis of the results provide a confidence with a degree of statistical certainty. By varying a single parameter and controlling all others, the simulation variance associated with each source of non-determinism can be found and addressed.

@@

\subsubsection{Sample Size}
% Tests should be sufficiently repeated using statistical power~\cite{cohen2013statistical} to reveal any outlier errors that occur with low probability.\todo[inline]{Explain what this means.} 
% Histogram to show how sampling with position binning varies?
% \footnote{\label{note1}Experiments using the Unreal Engine not reported here for brevity but code and experimental results can be found at \url{https://github.com/TSL-UOB/AV-Determinism/tree/master/UnrealEngineTests}}
%
% {\color{red} \sc Again, separate the study from the method. This observation should really have been made in the section on ``Experimental System Config and Pre-Screening, to justify the figure of 1000 repeats.} 
It is recommended that the chosen sample size is determined empirically. 
%
We recommend monitoring variance while increasing the sample size in orders of magnitude
until there is confidence that $\max\sigma$ will not exceed the permissible variance for the verification process. 
%
Note that we suggest monitoring the maximum value of $\sigma$, not the average, because if even a single simulation run is outside of the permissible variance this may lead to false confidence in the verification result.
